Preprocessing

### 2023-08-17 docs/presentation/preprocess.Rmd
viz: merge data

```{r data}
analysis <- readRDS("../../data/derived/public/analysis_hegs_rpr.rds")
source("data/constants.R")
```

@@

Q19: demographics

Potentially split into professor - not professor

```{r q19 groups}
analysis %>%
  group_by(Q19_recoded) %>%
  summarise(n = n())
```

@@

Q6
Q10
Q12a
Q15
Q17a

Potentially per group, but only for Q6

@@

```{r word clouds}
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
# saveRDS(clouds, file = "data/clouds.rds")
```

@@

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

@@

clouds_q10 <- append(clouds_q10_q3, clouds_q10_q4)
clouds_q10$Everyone <- clouds$Q10
# saveRDS(clouds_q10, file = "data/clouds_q10.rds")
```

@@

q8 <- append(q8_q3, q8_q4)
q8$Everyone <- q8_to_likert()
saveRDS(q8, file = "data/q8.rds")
```

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds")
```

>>>>

```{r data}
analysis <- readRDS("../../data/derived/public/analysis_hegs_rpr.rds")
source("data/constants.R")

gen <- list()
```

@@

@@

Potentially per group, but only for Q6 and Q10

@@

@@

gen$q6 <- append(clouds_q6_q3, clouds_q6_q4)
gen$q6$Everyone <- clouds$Q6
```

@@

gen$q10 <- append(clouds_q10_q3, clouds_q10_q4)
gen$q10$Everyone <- clouds$Q10
```

@@

gen$q8 <- append(q8_q3, q8_q4)
gen$q8$Everyone <- q8_to_likert()
```

## Save
```{r}
analysis %>%
  select(
    Q3_recoded, Q4, Q5,
    dat_rec, pro_rec, res_rec, con_rec, label,
    starts_with("Q7"),
    Q13_1, Q13_2,
    starts_with("Q9"),
    starts_with("Q14"),
    starts_with("Q17_")
  ) %>%
  saveRDS("data/analysis.rds")

gen %>%
  saveRDS("data/generated.rds")
```
